### 2013-11-13 inst/doc/README.Rmd
updated README

```{r echo=FALSE}
opts_knit$set(upload.fun = socialR::flickr.url)
opts_chunk$set(tidy=FALSE, warning=FALSE, cache=FALSE)
```

@@

```{r}
library(RNeXML)
f <- system.file("examples", "trees.xml", package="RNeXML")
nexml <- nexml_read(f)
tr <- get_tree(nexml) # or: as(nexml, "phylo")
plot(tr)
```

@@

```{r } 
get_taxa(nexml)
get_metadata(nexml) 
```

@@

@@

```{r}
modified <- new("meta",
                 property = "prism:modificationDate",
                 content = "2013-10-04")
```

@@

```{r}
website <- new("meta", 
               href = "http://carlboettiger.info", 
               rel = "foaf:homepage")
```

@@

```{r }
  history <- new("meta", 
      property = "skos:historyNote", 
      content = "Mapped from the bird.orders data in the ape package using RNeXML",
      id = "meta123")
```

@@

```{r}
  nexml_write(bird.orders, 
              file = "example.xml", 
              additional_metadata = list(history, modified, website), 
              additional_namespaces = c(skos = "http://www.w3.org/2004/02/skos/core#",
                                        prism = "http://prismstandard.org/namespaces/1.2/basic/",
                                        foaf = "http://xmlns.com/foaf/0.1/"))

>>>>

```{r echo=FALSE}
opts_knit$set(upload.fun = socialR::flickr.url)
opts_chunk$set(tidy=FALSE, warning=FALSE, message=FALSE, cache=FALSE)
```

@@

```{r}
library(RNeXML)
f <- system.file("examples", "trees.xml", package="RNeXML")
nexml <- nexml_read(f)
tr <- get_tree(nexml) # or: as(nexml, "phylo")
plot(tr[[1]])
```

@@

```{r } 
birds <- nexml_read("test.xml")
get_taxa(birds)
get_metadata(birds) 
```

@@

```
By default, `RNeXML` adds certain metadata, including the NCBI taxon id numbers for all named taxa.  This acts a check on the spelling and definitions of the taxa as well as providing a link to additional metadata about each taxonomic unit described in the dataset.

@@

```{r}
modified <- meta(property = "prism:modificationDate",
                 content = "2013-10-04")
```

@@

```{r}
website <- meta(href = "http://carlboettiger.info", 
                rel = "foaf:homepage")
```

@@

```{r }
  history <- meta(property = "skos:historyNote", 
                  content = "Mapped from the bird.orders data in the ape package using RNeXML",
                  id = "meta123")
```

@@

```{r}
  nexml_write(bird.orders, 
              file = "example.xml", 
              additional_metadata = list(history, modified, website), 
              additional_namespaces = c(skos = "http://www.w3.org/2004/02/skos/core#",
                                        foaf = "http://xmlns.com/foaf/0.1/"))
